Tree height, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2019-09-21 manuscript/climate_sensitivity_draft.Rmd
minor edits

*Key words*:  canopy position; drought; hydraulic traits; microhabitat; temperate broadleaf deciduous forest;  tree growth; tree height; tree-ring [5-8] *Five to eight key words (in alphabetical order) . Words that are in the title can, and should, be among these. Very short phrases and scientific names with their common equivalents (e.g. Nicotiana tabacum (tobacco)) are acceptable.*

>>>>

*Key words*:  canopy position; drought; Forest Global Earth Observatory (ForestGEO); hydraulic traits; temperate broadleaf deciduous forest;  tree growth; tree height; tree-ring [5-8] *Five to eight key words (in alphabetical order) . Words that are in the title can, and should, be among these. Very short phrases and scientific names with their common equivalents (e.g. Nicotiana tabacum (tobacco)) are acceptable.*
